Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-28 paper.tex
minor edit

Set $g(n,l)$ to be $\frac{l}{n}$. Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm. Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{2m}{p^{-1}(\frac{p}{2})}$. In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2m}$, we need $n\geq \lceil a_{0} l\rceil$. In order to hvae $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Thus, we know we can only incur regret in the $l^{th}$ envelope in the first $\max\{n_1,\lceil a_0 l\rceil\}$ rounds.

>>>>

Set $g(n,l)$ to be $\frac{l}{n}$. Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm. Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{2m}{p^{-1}(\frac{p}{2})}$. In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2m}$, it is sufficient to have $n\geq \lceil a_{0} l\rceil$. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_1,\lceil a_0 l\rceil\}$ rounds.
